Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-22 main.tex
editing rel. work section (II-B done)

    \subsection{Memory-aware scheduling algorithms}
    Respecting processor memories adds a constraint to a scheduling problem.
    Therefore, only specifically memory-targeted algorithms address this issue.
    Moreover, the way processor memories are represented in the model has a decisive impact on the way the constraint
    is formulated and addressed in the algorithm.
%
    Different models of memory available on processors and memory requirements of tasks have been presented.

    Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
    Workflow tasks have no memory requirements, but they have input and output files that need to be stored in the memory.
    A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a DAG is provided,
    as well as an ILP solution to the scheduling problem.
    The memory model requires deleting all input data upon starting of the task and adding all output files there.

    In an assumed dual-memory systems~\cite{herrmann2014memory},  a processor can have access 
    to a memory of two different
    kinds (red or blue), and each task can be executed on only one sort of memory.
    The communications happen only between these two kinds of processors (communications within 
    each group are ignored).
    The authors then formulate an ILP solution for this problem formulation.

@@

    In~\cite{ding2024ils}, there are connected processors with individual limited memories.
    The collective set of memories forms the global memory, to which each processor has access, however the access time
    to global memory is different.
    Each memory access in the graph is modeled as a memory access token on the task, while the edges have no weights.
    The solved problem is how to allocate initial input data in processor memories so that the overall
    execution is minimized and the memories are not exceeded.
    The authors propose an integer linear programming model.
    %that minimizes the length of the critical path, including a greedy initial solution.

    In~\cite{rodriguez2019exploration}, the authors assume memory requirement on tasks represented as tiles.
    Each processor has individual memories to process the task, but only the shared memories store the tiles containing
    memory tiles occupied by memory tiles.

@@

   Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
   platform that is fully heterogeneous, with individual memories, is the one from~\cite{DBLP:conf/icpp/KulaginaMB24},
   but where a partition of the workflow is proposed, hence preventing processor reuse. 
   Hence, in ~\cite{DBLP:conf/icpp/KulaginaMB24}, there is no need of communication buffers to store data 
   that should be communicated
   between two processors when tasks are ready to execute.

>>>>

\subsection{Memory-aware scheduling algorithms}
\label{sub:mem-aware-algs}
%
Only memory-aware scheduling algorithms are designed to respect memory constraints.
%Respecting processor memories adds a constraint to a scheduling problem.
%Therefore, only specifically memory-targeted algorithms address this issue.
Moreover, the way processor memories are represented in the model has a decisive impact on the way the constraint
is formulated and addressed in the algorithm.
%
Different models of memory available on processors and memory requirements of tasks have been presented.

Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
Workflow tasks have no memory requirements, but they have input and output files that need to be stored in the memory.
A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a workflow DAG is provided,
as well as an integer linear programming (ILP) solution to the scheduling problem.
The memory model requires the deletion of all input files when starting the task.
% and adding all output files there.
% TODO: This sounded strange. I changed ``input data'' to ``input files''.
% How can I process input data when they are deleted? 
% TODO: And what is ``there''?

In an assumed dual-memory system~\cite{herrmann2014memory},  a processor can have access 
to two different kinds of memory, and each task can be executed on only one sort of memory.
Communication happens only between these two kinds of processors (communication within 
each group is ignored).
The authors then present an ILP-based solution for this problem formulation.

@@

In~\cite{ding2024ils}, the authors consider connected processors with individual limited memories.
The collective set of memories forms the global memory to which each processor has access;
however, the access time to global memory is different.
Each memory access in the graph is modeled as a memory access token on the task, while the edges have no weights.
The solved problem is how to allocate the initial input data in processor memories so that the overall
execution is minimized and the memories are not exceeded.
To this end, the authors propose an ILP model.
%that minimizes the length of the critical path, including a greedy initial solution.

In~\cite{rodriguez2019exploration}, the authors assume memory requirements on tasks represented as tiles.
Each processor has individual memories to process the task, but only the shared memories store the tiles containing
memory tiles occupied by memory tiles.

@@

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, is the one from~\cite{DBLP:conf/icpp/KulaginaMB24}.
Yet, they propose only a partitioning-based mapping of the workflow without processor reuse.
Hence, in~\cite{DBLP:conf/icpp/KulaginaMB24}, there is no need for communication buffers to store data 
that should be communicated between two processors when tasks are ready to execute. 
% TODO: Why is the last sentence necessary? More specifically, why is it a consequence of the previous
% sentence (as implied by ``Hence''?)?
